Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-06-20 paper/document.tex
Latest revision of the paper

When managing group projects in an introductory software engineering course, it is very important to be able to see the contributions that students are making to the group repository to judge learning, progress, and collaboration. When one of the authors was supervising 4--5 groups of students, it became infeasible to look through all of the commits of each student. Students may take the wrong approach in a certain piece of code that can become ingrained in the project and very difficult to change. Some groups had problems with group members who did not complete their assigned work or made meaningless contributions. Issues like this can be difficult to detect and prevent. TypeV was used by the author to quickly summarize the work done by each group member, organized by the types they had been working on. This can show when intervention or guidance is required, without the large time commitment of pouring through commits.

@@

@@

Currently, we treat every instance of a generic type as a different type. For example, considered the \texttt{List<T>} generic class in Java. If a user declares a List of Strings and later declares a List of Integers these will appear as two different types in TypeV. However, if they declare multiple instances of a List of Strings then these instances will count toward the same type. In the future, we want to work on a better way to track and represent generic types.

>>>>

@@

An external threat to validity is the limited number of projects used in the validation. We picked curated projects that had a long development cycle and looked into some case studies. However, because of the limited number of projects we observed, our conclusions may not hold for the majority of software projects.

@@
